---
title: "Regression solution"
author: "Oleksii Yehorchenkov"
date: "09 03 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

This is assignment is inspired by practices of [Ryan Miller] (https://remiller1450.github.io/).

## Using regression for predicting binary outcome.

The [Donner Party](https://en.wikipedia.org/wiki/Donner_Party) dataset documents the fate of members of the Donner Party, a group of 45 pioneers whose migration to California was delayed by a series of mishaps which resulted in the group being stranded in the Sierra Nevada mountains. You can find `donner_party.csv` in the `data` folder.

**Problem**
Predict survival status members of the Donner Party. The target variable is `Survived`.

## Task

Read the data. Pay attention that data has NA values. It's better to convert target variable to factor.
```{r}
# code for reading data

```

For prediction we will use only variables `Sex` and `Age`. 

For predicting binary outcome we will use **Generalized Linear Model** (`method = "glm"`) and **caret package**. 

```{r}
# code for regression


```

What is your in-sample accuracy? Build a confusion matrix

```{r}
# code for confusion matrix

```
Use a cross-validation with `method = "repeatedcv"`, `number = 5`, `repeats = 10`. Does cross-validation improve the accuracy?

```{r}
# code for cross-validation


```
